---
title: "nupic: Platform for Intelligent Computing"
output:
  github_document:
    fig_width: 8
    fig_height: 4
---

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  fig.path = "tools/readme/", 
  dev = "png",
  dpi = 96,
  comment = "#>",
  collapse = TRUE
)

ggplot2::theme_set(ggplot2::theme_light())
```

This R packages provides an interface to the Numenta Platform for Intelligent Computing **(NuPIC)**, a machine intelligence platform that implements the [HTM learning algorithms](https://numenta.com/resources/papers-videos-and-more/). HTM is a detailed computational theory of the neocortex. At the core of HTM are time-based continuous learning algorithms that store and recall spatial and temporal patterns. NuPIC is suited to a variety of problems, particularly anomaly detection and prediction of streaming data sources. For more information, see [numenta.org](http://numenta.org/), the [NuPIC Forum](https://discourse.numenta.org/c/nupic) and [documentation](http://nupic.docs.numenta.org/).

## Installation 

First, install the latest GitHub version:

```{r, eval = FALSE}
remotes::install_github("javierluraschi/nupic")
```

Followed by installing the Nupic runtime:

```{r setup}
nupic::nupic_install()
```

**Note**: Nupic requires Python to be installed in your system.

## Usage

```{r}
library(nupic)

nupic(
  gym_hourly[1:10,],
  predict = "consumption",
  encoders = nupic_config_en(
    encoder_random_distributed_scalar("consumption", resolution = 0.88, seed = 1),
    encoder_date("timestamp", "time_of_day", time_of_day = list(21L, 1L)),
    encoder_date("timestamp", "weekend", weekend = 21L)
  )
)
```


